<style>
.main-container {
    max-width: 1324px;
    margin-left: 10px;
    margin-right: auto;
}
</style>

<style type="text/css">
   .main-container {max-width: 1324px;}
   .row {display: flex;}
   .column {flex: 700;}
</style>

<style>
    table {
      border-collapse: collapse; /* Ensures borders don't overlap */
      width: 100%; /* Optional: makes the table take the full width */
    }
    th, td {
      border: 1px solid black; /* Adds borders to cells */
      padding: 10px; /* Adds padding around text */
      text-align: left; /* Aligns text to the left inside cells */
    }
    th {
      background-color: #f2f2f2; /* Optional: gives header cells a background color */
    }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(data.table)
library(dplyr)
library(tidyverse)
library(yaml)
library(DT)
library(stringr)
```

```{r meta_configs, include=FALSE}

meta <- read.csv(paste0('../../samples.sample_list'), sep = '\t', header = TRUE)
#meta <- read.csv(paste0('samples.sample_list'), sep = '\t', header = TRUE)
meta <- meta[, c(1, 2)]
#samples <- meta$samples


# Read in configs
proj_info <- read_yaml(paste0('../../configs/local_configs.yaml'))
final_info <- read_yaml(paste0('../../configs/final_configs.yaml'))
#proj_info <- read_yaml(paste0('../../configs/local_configs_dicer_test.yaml'))
#final_info <- read_yaml(paste0('../../configs/final_configs_dicer_test.yaml'))

## Main project info
project <- proj_info$`PROJECT`   
organism <- proj_info$`ORGANISM`

## Configs relevant to rules + processing time
run_cellranger <- proj_info$`RUN_CELLRANGER`
create_bam <- proj_info$`OUTPUT_BAM`
run_multiqc <- proj_info$`RUN_MULTIQC`
run_soupX <- proj_info$`RUN_SOUPX`
run_doubletFinder <- proj_info$`RUN_DOUBLETFINDER`
components <- proj_info$`COMPONENTS`
num_var_features <- proj_info$`NUM_VARIABLE_FEATURES`
scale_data_features <- proj_info$`SCALE_DATA_FEATURES`
mito_regression <- proj_info$`MITO_REGRESSION`
ribo_regression <- proj_info$`RIBO_REGRESSION`
regression_file <- proj_info$`REGRESSION_FILE`
cell_cycle_regression <- proj_info$`CELL_CYCLE_REGRESSION`
cell_cycle_method <- proj_info$`CELL_CYCLE_METHOD`
seurat_normalization_method <- proj_info$`SEURAT_NORMALIZATION_METHOD`
seurat_integration_method <- proj_info$`SEURAT_INTEGRATION_METHOD`
reference_based_integration <- proj_info$`REFERENCE_BASED_INTEGRATION`
reference_samples <- proj_info$`REFERENCE_SAMPLES`
run_azimuth <- proj_info$`RUN_AZIMUTH`
azimuth_reference <- proj_info$`AZIMUTH_REFERENCE`
run_transferdata <- proj_info$`RUN_TRANSFERDATA`
transferdata_ref_file <- proj_info$`TRANSFERDATA_REF_FILE`
transferdata_reduction <- proj_info$`TRANSFERDATA_REDUCTION`
transferdata_annocol <- proj_info$`TRANSFERDATA_ANNOCOL`
resolution <- proj_info$`RESOLUTION`
tsne <- proj_info$`TSNE`
conserved_genes <- proj_info$`CONSERVED_GENES`
storage <- proj_info$`STORAGE`
threads <- proj_info$`THREADS`
memory <- proj_info$`MEMORY`
user_gene_file <- proj_info$`USER_GENE_FILE`
visualization <- proj_info$`VISUALIZATION`

#Final Analysis
final_visualization <- final_info$`FINAL_VISUALIZATION`
trajectory <- final_info$`RUN_TRAJECTORY_ANALYSIS`
final_storage <- final_info$`FINAL_STORAGE`
final_conserved_genes <- final_info$`FINAL_CONSERVED_GENES`
final_threads <- final_info$`FINAL_THREADS`
final_user_gene_file <- proj_info$`FINAL_USER_GENE_FILE`

# read in benchmark table & images
benchmark_dir <- paste0('../../data/endpoints/', project, '/analysis/report/benchmarks/')
benchmark_table_dir <- paste0(benchmark_dir, 'table/')
benchmark_fig_dir <- paste0(benchmark_dir, 'figures/')

benchmark_file <- paste0(benchmark_table_dir, project, '_benchmarks.txt')
benchmarks <- read.table(benchmark_file, header=TRUE, sep='\t')

time_memory <- paste0(benchmark_fig_dir, project, '_time_memory.png')
in_out_file <- paste0(benchmark_fig_dir, project, '_in_out.png')
```

---
showWarnings: FALSE
title: "`r project`"
subtitle: "Benchmarking Report"
date: "`r format(Sys.time())`"
output: html_document
---

<div class = "main-container">

# Pipeline Information
SWANS, version 2.0

## YAML Configuration Parameters
##### Species
Organism: `r organism`

##### Initial Processing
Was CellRanger Run? `r run_cellranger`   
If yes, were bam files created? `r create_bam`   
Was a MultiQC report created with CellRanger output? `r run_multiqc`  
Was SoupX Run? `r run_soupX`    
Was DoubletFinder Run? `r run_doubletFinder`    

How many PCA components were initially investigated? `r components`  
How may variable features were used? `r num_var_features`   
How was the data scaled? `r scale_data_features`   

Were mitochondira genes regressed out? `r mito_regression`   
Were ribosomal genes regressed out? `r ribo_regression`   
Were cell cycling genes regressed out? `r cell_cycle_regression`   
Name of user-supplied file containing additional genes to regress out? `r regression_file`  

Normalization Method(s): `r seurat_normalization_method`  
Integration Method(s): `r seurat_integration_method`  
Resolution(s): `r resolution`  

Reference-Based Integration? `r reference_based_integration`  
Reference-Based Samples: `r reference_samples`  

Was Azimuth Run? `r run_azimuth`    
Were lables transferred from an additional seurat object? `r run_transferdata`    
Was Azimuth Run? `r run_azimuth`    

Was FindConservedMarkers run? `r conserved_genes`  
Was tSNE used? `r tsne`  

How was the data stored? `r storage`  
How many threads were used for parallel processing? `r threads`  
Max assigned memory? `r memory`  

Did user supply additional genes for visualization? `r user_gene_file`  
How did they want the additional genes visualized? `r visualization`  

 *** 
 
##### Final Processing
Was Trajectory Analysis Run? `r trajectory`    
How many threads were used for parallel processing? `r final_threads`  
How was the final data stored? `r final_storage`  
Were conserved genes found? `r final_conserved_genes`  
Name of user-supplied file containing (final) genes for visualization? `r final_user_gene_file`  
How were they visualized? `r final_visualization`  

 *** 

## Sample Information
```{r samples, echo=FALSE, include=TRUE}
datatable(data = meta, caption = 'Table 1: Sample Data.', options=list(pageLength=20))
```

 *** 

## Benchmarks
```{r zscore_c_experiment, include=T, echo=F, out.width="100%", warning=FALSE}
datatable(data=benchmarks, class = 'cell-border stripe', caption = 'Table 2: Benchmarking results for all Snakemake Rule', rownames= FALSE, filter = 'top', extensions = 'Buttons', width = '100%', options = list(autoWidth = TRUE, pageLength=30, dom = 'Blfrtip', buttons = c('colvis', 'copy', 'excel', 'pdf', 'print')))
```

<div class = "row">
<div class = "column">
```{r tm, include=T, echo=F, out.width="100%", out.height="100%", fig.cap='Figure 1: Running time (hour:minutes:seconds) vs Max Physical Memory'}
  knitr::include_graphics(time_memory)
```
</div>

<div class = "column">
```{r in_out, include=T, echo=F, out.width="100%", out.height="100%", fig.cap='Figure 2: Number of MB read vs Number of MB written'}
   knitr::include_graphics(in_out_file)
```
</div>
</div>

#### psutil description
<table border="1">
  <thead>
    <tr>
      <th>colname</th>
      <th>type (unit)</th>
      <th>description</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>s</td>
      <td>float (seconds)</td>
      <td>Running time in seconds</td>
    </tr>
    <tr>
      <td>h:m:s</td>
      <td>string (-)</td>
      <td>Running time in hour, minutes, seconds format</td>
    </tr>
    <tr>
      <td>max_rss</td>
      <td>float (MB)</td>
      <td>Maximum "Resident Set Size”, this is the non-swapped physical memory a process has used.</td>
    </tr>
    <tr>
      <td>max_vms</td>
      <td>float (MB)</td>
      <td>Maximum “Virtual Memory Size”, this is the total amount of virtual memory used by the process</td>
    </tr>
    <tr>
      <td>max_uss</td>
      <td>float (MB)</td>
      <td>“Unique Set Size”, this is the memory which is unique to a process and which would be freed if the process was terminated right now.</td>
    </tr>
    <tr>
      <td>max_pss</td>
      <td>float (MB)</td>
      <td>“Proportional Set Size”, is the amount of memory shared with other processes, accounted in a way that the amount is divided evenly between the processes that share it (Linux only)</td>
    </tr>
    <tr>
      <td>io_in</td>
      <td>float (MB)</td>
      <td>the number of MB read (cumulative).</td>
    </tr>
    <tr>
      <td>io_out</td>
      <td>float (MB)</td>
      <td>the number of MB written (cumulative).</td>
    </tr>
    <tr>
      <td>mean_load</td>
      <td>float (-)</td>
      <td>CPU usage over time, divided by the total running time (first row)</td>
    </tr>
    <tr>
      <td>cpu_time</td>
      <td>float(-)</td>
      <td>CPU time summed for user and system</td>
    </tr>
  </tbody>
</table>

<br>&nbsp;<br>



</div>
